The aim of this master’s thesis is to design and implement a new approach of the fast optimization specifically oriented on the model predictive control. Methodology is based on the distribution of the optimization problem into smaller sections, in model predictive control this means split cost function respect to each step of the prediction horizon. Later we used distributed optimization algorithm with the possibility of a parallel solving and we apply this method on the model predictive control with linear and nonlinear model of the system. In the practical part of this thesis the theory was tested by using simulations in order to determine whether the computational time of the controller will be improved or not. In the last part of this thesis we developed application which allow us to use this kind of model predictive control. The application was divided into two parts. The first one is server which help us to build whole web application. The server is used for data management and for creating a distributed optimization problem. The second part located in the web interface is designed for users whose can use it for defining system and controller parameters. Numerical optimization performed on the background of this interface is used to find minimum of distributed optimization problem. The way  how the application was  designed support parallel solving on multiple computing devices.\\
\textbf{Key words:} model predictive control, distributed optimization algorithm, web application, numerical optimization
